Gender and Mental Depression: Analyzing Census Data Through Statistical Methods

### 2024-10-23 paper/paper.qmd
Conclusion added by Christina.

>>>>

# Conclusion

This paper presented an overview of the educational attainment, sex, and psychological distress among participants. By looking at the Kessler 6 Scale for nonspecific psychological distress (K6SUM), we found complex relationships between education, sex, and mental health in the United States for our population. Firstly, the data revealed significant trends in educational attainment, highlighting disparities that exist among different demographic groups. Our constructed variable, EDUC, provided a clear understanding of individuals' highest completed education level through group lumping, which is important for identifying populations at risk of lower socioeconomic status. This knowledge can help inform targeted educational interventions and policies aimed at improving access to higher education, such as increasing funding for scholarships and grants for underrepresented groups, expanding community college programs, implementing outreach initiatives in underserved areas, providing mentorship opportunities, and enhancing financial literacy programs to help prospective students navigate the college application and funding processes.
